%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Experience}

%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}
\vspace{-3mm}
%---------------------------------------------------------
  \cventry
    {Principal Engineer} % Job title
    {HypergameAI} % Organization
    {Remote} % Location
    {Sept. 2024 - Present} % Date(s)
    {
      \begin{cvitems}
        \item {
          Led development of multiple cyber security deception products, including a honeypot system for simulated cryptocurrency wallets and implemented intentional SSRF vulnerabilities with automated threat detection and decoy deployment capabilities.
        }
        \item {
          Architected and implemented cloud infrastructure using Terraform and Helm charts for GCP resources, including GKE clusters, CloudSQL, Firestore, and Artifact Registry, ensuring scalable and secure deployment of deception platform components.
        }
        \item {
          Developed a novel decoy object generation service using FastAPI and LLaMA 3 models, creating realistic decoy Word, Excel, and PDF documents for cyber range environment seasoning, improving the authenticity of deception scenarios.
        }
        \item {
          Was instrumental in building a cyber security range generation platform with integrated authentication. This platform allowed users to generate and test range scenarios in an isolated playground and automatically deploy containerized services to Kubernetes.
        }
        \item {
          Established and standardized development processes by implementing structured Epic/Story templates and organizing the product backlog while managing infrastructure across AWS and GCP environments.
        }
        \item {
          Identified and remediated critical security vulnerabilities through both automated security tooling and manual testing, including hard-coded credential exposure and XSS vulnerabilities within LLM-integrated components.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Staff Security Engineer} % Job title
    {Quickbase} % Organization
    {Remote} % Location
    {Sept. 2020 – Sept. 2024} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Deployed and configured CodeQL, Mend, and Lacework Infrastructure as Code (IaC) scanning using GitHub Actions and Jenkins. These tools support the scanning of C++, C\#, Python, Java, and JavaScript repositories.
        }
        \item {
          Managed the implementation of Lacework across public cloud providers, seamlessly integrating it with CSPM, CloudTrail, and Audit Logs. Utilized IaC to automate Lacework agent and agentless deployments, monitoring all hosts and containers for vulnerabilities, malware, and user behavioral anomalies.
        }
        \item {
          Built Tines SOAR automation to enrich alerts from Lacework with important information and context. This enriched data is then leveraged to initiate automated workflows, resulting in targeted Slack notifications and efficient Jira ticket creation.
        }
        \item {
          Designed and implemented vulnerability management automation using Tines to process findings from Lacework and Mend. This reduced the organization's overall vulnerability exposure by 89\%.
        }
        \item {
          Directed annual pentests utilizing external pentesting firms. Provisioned testing environments, configured access, managed communication, and triaged/reproduced vulnerabilities. Created tickets to remediate all legitimate findings and worked with development teams to identify false positives.
        }
        \item {
          Modernized responsible disclosure program by working with internal stakeholders to build a standardized and scalable process. This resulted in faster response times, better lines of communication internally, and higher quality analysis of reported findings.
        }
        \item {
          Acted as security engineering Team Lead, overseeing and mentoring two junior security engineers. Conducted training sessions, assigned daily tasks, and provided guidance to foster their professional growth within the security domain.
        }
        \item {
          Collaborated with DevOps to migrate containerized services to hardened golden images, using secure base images and incorporating security best practices. This allows developers to focus on building applications, while ensuring a secure foundation for their work.
        }
        \item {
          Wrote automation to scan new Docker images with Lacework in both Artifactory and Jenkins pipelines, shifting left Docker image scanning and allowing Jenkins pipelines to block new Docker images that violate policies.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Senior DevSecOps Engineer} % Job title
    {NetNumber} % Organization
    {Remote} % Location
    {May 2020 – Sept. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Quickly developed a thorough understanding of the engineering environment, product stack, code base, and identified security needs.
        }
        \item {
          Integrated SonarQube and Snyk into Jenkins CI/CD pipelines.
        }
        \item {
          Managed vulnerabilities found using DevSecOps tools and worked with development teams to remediate them.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Application Security Engineer} % Job title
    {Schneider Electric} % Organization
    {Andover, Massachusetts} % Location
    {May 2018 – May 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Worked within a SAFe scrum development environment to integrate security engineering into the constant delivery of SaaS software.
        }
        \item {
          Completed penetration tests, worked on threat models with developers and architects, and completed Security SDLC documentation.
        }
        \item {
          Managed cyber security processes for four development teams.
        }
        \item {
          Wrote CI/CD pipelines to complete Static Application Security Testing (SAST) scanning.
        }
      \end{cvitems}
    }

%---------------------------------------------------------
  \cventry
    {Information Security Consultant} % Job title
    {GraVoc} % Organization
    {Peabody, Massachusetts} % Location
    {May 2017 – May 2018} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {
          Independently completed penetration testing, vulnerability assessments, social engineering engagements, and risk assessments.
        }
        \item {
          Crafted tailored exploits for social engineering engagements based on the client's infrastructure.
        }
        \item {
          Traveled to client sites to perform security testing and auditing.
        }
      \end{cvitems}
    }
\end{cventries}
